Computing the bicharacter of huge subspaces of polynomials

### 2019-06-21 article/article.tex
Rereading

	\section{Introduction}
	The development of this package started at the occasion of a collaboration with François Bergeron to study the character of the space $\harmonics_n^{(r)}$ of diagonal harmonic polynomials on $r$ sets of $n$ variables, as a graded bi-$\GLr \times \Sn$-module. It was then extended to compute other character on polynomials spaces. The main achievement is a calculation of this character of the diagonal harmonic polynomials for $n=6$ \pauline{+ some cases for $n=7$} and $r=5$ (and therefore any $r$) in 45 minutes (and ~15Gb), which led to conjectures on its general value.

@@

	Consider the polynomial ring $R=\QQ[X]$ with $r$ sets of $n$ variables. To fix conventions, we think of $X$ as a matrix of variables:
	$$(x_{i,j})_{0\leq i<r \atop 0\leq j<n}$$
	and we denote by $\bm{x}_i = (x_{i1}, x_{i2}, \dots, x_{in})$ the i-th set of variables. We use the convention that bold letters stand for sets of variables and light letters stand for the variables themselves.

	The polynomial ring $R$ is endowed with an action of the symmetric group $\Sn$ by diagonal permutation of the columns and of the general linear group $\GLr$ by diagonal action on the rows. The invariant ring $R^{\Sn}$ is also known as the ring of multisymmetric functions, that is to say the elements of $R$ that remain unchanged under permutations of the rows of $X$. The co-invariant ring $R_{\Sn}$ is the quotient of $R$ by the ideal $\mathcal{I}_n = \langle {R^{\Sn^+}} \rangle$ of the multisymmetric functions without constant term. It inherits from $R$ a structure of graded $\GLr \times \Sn$ bi-module.

	The grading can be refined into a multigrading by rows. The multigrading is preserved by the action of $\Sn$. The multigrading is not preserved by the action of $\GLr$, but instead carries exactly the information about the $\GLr$ character. It's thus equivalent to consider the $\GLr \times \Sn$ bicharacter or the $\Sn$ multigraded character of $R_{\Sn}$.

@@

	Throughout this article, we implicitly use the Frobenius map, and identify $\Sn$ and $\GLr$ irreducible characters with their associated Schur symmetric functions. \\

	We denote the partial derivatives the following way $\partial^k_x := \frac{\partial^k}{\partial x^k}$ for all variables $x \in X$.
	When $X$ contains only one set of variables ($r=1$), $X = (x_1, x_2, \dots, x_n)$, we define the \emph{harmonic polynomials} as follow.

	\begin{definition}
		Let $f \in R$, $f$ is \emph{harmonic} if and only if, for all $k \geq 0$, $k \in \NN$,
		$$\partial^k_{x_1} f + \partial^k_{x_2} f + \dots + \partial^k_{x_n} f = 0.$$
	\end{definition}

	For example the Vandermonde determinant $V_n:= \det(x_i^a)_{1 \leq i \leq n \atop 0 \leq a \leq n-1} = \prod_{i<j}(x_i-x_j)$ is harmonic.

	The space of harmonic polynomials in $n$ variables, denoted $\harmonics_{n}$ is the joint kernel of the differential operators $D_k := \partial_{x_1}^k + \cdots + \partial_{x_n}^k$. It is also a realization of the coinvariants of the symmetric group: $R\, /\, \langle Sym(X)^+ \rangle$ and a graded regular representation of $\Sn$.

	For example, $\harmonics_2 = \langle 1, x_1-x_2 \rangle_\QQ$.

@@

	Going back to an arbitrary number $r$ of sets of variables, we define the \emph{differential operators} $(D_\alpha)_{\alpha\in \NN^r}$:
	$$D_{(\alpha_1, \dots, \alpha_r)} := \partial_{x_{11}}^{\alpha_1}\dots\partial_{x_{r1}}^{\alpha_r} + \dots + \partial_{x_{1n}}^{\alpha_1}\dots\partial_{x_{rn}}^{\alpha_r} = \sum_{j=1}^{n} \prod_{i=1}^{r} \partial_{x_{ij}}^{\alpha_i}$$

	For example, take $r=3$ and denote $\bm{x}, \bm{y}$ and $\bm{z}$ the three sets of variables of $X$, then $D_{(3,0,4)} := \partial_{x_1}^3\partial_{z_1}^4 + \dots + \partial_{x_n}^3\partial_{z_n}^4$.

@@

	As for the harmonics, we have an alternative way to obtain $\harmonics_n^{(r)}$ directly using operators.

@@

	Let $\bm{x}=(x_1, x_2, \dots, x_n)$ and $\bm{y}=(y_1, y_2, \dots, y_n)$ be two sets of variables and $\mu$ be a partition of $n$. We also denote $\mu$ the Ferrer's diagram (in French notation) associated to the partition $\mu$ and each cell of $\mu$ is given by the Cartesian coordinates $(a,b)$ of its bottom left corner. Then, let define
	$$M_{\mu} := \det (x_i^ ay_i^ b)_{1 \leq i \leq n \atop (a,b) \in \mu}$$
	and the Gasia-Haiman module associated to $\mu$ is the smallest subspace containing $M_{\mu}$ and closed under differentiation for both sets of variables. \\

	With a similar idea, François Bergeron recently introduced another generalization of the diagonal harmonics, with \emph{inert variables}. We add a new row $\bm{\theta} = (\theta_1, \theta_2, \dots, \theta_n)$ of variables in $X$ and call them inert. The symmetric group still acts diagonally on the columns of $X$, but $GL_r$ now acts only on the rows containing non-inert variables.

@@

	We first need to compute in a quotient by an ideal, $R / \mathcal{J}_n$ where $\mathcal{J}_n$ is the ideal of diagonal symmetric polynomials on $r$ sets of $n$ variables. \pauline{$\langle Sym(X)^+ \rangle$ ?}
	A standard approach would be to compute a Gröbner basis of this ideal.
	We haven't actually tried it, but given the number of variables and dimension of the quotient, we expect this calculation to be intractable.

@@

	At this stage, we have an algorithm, but are still doing linear algebra in a huge space (cost $N^2 M$, where $N$ is the dimension of the result and $M$ the dimension of the ambient space).

@@

	\begin{example} Compute $\mathcal{E}_{2,1}^{(2)}$ using the multidegree. 
		\begin{sagesilent}
			load("../compute_character.py")
		\end{sagesilent}
		First, we compute $\mathcal{E}_{2,1}^{(1)}$, for one row of variables. 
		\begin{sagecommandline}
			sage: v = vandermonde(Partition([2,1]))
			sage: v
			sage: derivatives = partial_derivatives(v.parent())
			sage: derivatives
			sage: E_21 = Subspace({v.multidegree(): [v]}, derivatives)
			sage: E_21.basis()
			sage: E_21.dimension()
		\end{sagecommandline}
		Then, we use polarization operators to introduce a second set of variables, and thus obtain $\mathcal{E}_{2,1}^{(2)}$, still with multidegree. 
		\begin{sagecommandline}
			sage: polarizators = polarization_operators(2)
			sage: polarizators
			sage: E_21 = PolarizedSpace(E_21, polarizators)
			sage: E_21.basis()
			sage: E_21.dimension()
			sage: E_21.dimensions()
		\end{sagecommandline}
		Compared with example \ref{H_3} in which all basis elements are grouped in one list with key $0$, here basis elements are classified by multidegree with the key corresponding. Operators are also separated by multidegree. Moreover, we have access to dimension by multidegree. 
	\end{example}

@@

	The $\GLr$ character can easily be recover from the multigrading, but it remains to find an efficient way to compute the representations of $\Sn$. Computing the traces of the action of permutations of all cycle types would not be an option because of the dimension and the high number of terms of the polynomials. 
	Instead, we use an isotypic projector to obtain the isotypic components of $\Sn$ and from that we will be able to recover the irreducible characters of $\Sn$ and their multiplicities. \\

	We first define two elements of the symmetric group algebra $\CC \Sn$. Note that we use the cyclic notation for permutations.
	Let $P_{\mu}$ be the subgroup of $\Sn$ of all row preserving permutations of $\mu$ and $Q_{\mu}$ the subgroup of the columns preserving permutations of $\mu$. To determine the row and column preserving permutations, we consider the canonical Young tableau of $\mu$, that is to say to tableau filled in by integers from $1$ to $n$ in increasing order, from left to right and from bottom to top. 
	\begin{example} Consider $\Sym{3}$ and let $\mu = 2,1$.
		The canonical tableau associated is \tableau(12,3).\\
		Then $P_\lambda = \{1, (12)\}$ and $Q_\lambda = \{1, (13)\}$. \\
	\end{example}

@@

	\addtocounter{example}{-1}
	\begin{example} (end) 
		For $\mu=2,1$, we have
		$a_{2,1} = 1 + (12)$ and
		$b_{2,1} = 1 - (13)$.

@@

		For the other partitions of size $3$, one can verify that 
		$y_{111} = \sum_{\sigma \in \Sym{3}} \sigma$ and 
		$y_{3} = \sum_{\sigma \in \Sym{3}} \sgn(\sigma)\sigma$
	\end{example}

@@

	The proof of the above theorem is given by Fulton and Harris in \cite{FultonHarris1991}. 
	This theorem guarantees that $c_{\lambda}$ is an isotypic projector and that applying it on the elements of $\mathcal{E}_{\lambda}$ gives representatives of the isotypic components of $\Sn$. \pauline{Need more details here!}  \\

@@

	However, for all $v \in \mathcal{E}_\lambda$, $v$ is anti-symmetric with respect to the column stabilizer $Q_\mu$, with $\mu$ the type of the isotypic component of $v$. Indeed, when projecting $v$ on its isotypic component using the Young idempotent $c_\mu$, by definition $a_\mu$ makes any element symmetric with respect to the row preserving permutations of $\mu$ and then $b_\mu$ makes the result anti-symmetric with respect to the column preserving permutations of $\mu$. 
	It's therefore sufficient to keep one representative monomial per $S_P$ orbit \pauline{$S_P$ orbit?} (and do some appropriate straightening whenever a new monomial is created). We chose to keep the smallest representative monomial in lexicographic order and call the result the normal reduced form of $v$. \\

@@

		$\Delta_{21} = -x_{2} \theta_{1} + x_{3} \theta_{1} + x_{1} \theta_{2} - x_{3} \theta_{2} - x_{1} \theta_{3} + x_{2} \theta_{3}$ is type $1,1,1$.
		Reduced form : $x_1\theta_2$.

		$\partial_{x_2}\Delta_{21} = -\theta_1 + \theta_3$ is type $2,1$. 
		Reduced form : $-\theta_1$ 
	\end{example}

@@

	To achieve this, polarization operators can be tweaked: whenever the result of a polarization is not of decreasing multidegree, straighten it by applying an appropriate permutation of the rows. It can then easily be shown that those tweaked polarization operator properly generate the whole $\mathcal{E}_\lambda^{(r)}$ space from $\mathcal{E}_\lambda^ {(1)}$.

@@

	In practice, we exploit the row symmetries when we set up the polarization operators. As said above, when specifying the row symmetries, only components of decreasing multidegree appear in the final result.

@@

	As said before, the character of $\GLr$ is given by the multidegree of the homogeneous components. In other words, for a given isotypic component of type $\mu$, the $\GLr$-character associated to this component is given by $\sum_{\mathcal{E}} q^{d(\mathcal{E})}$ where the sum is over all homogeneous $\mathcal{E}$ component of type $\mu$, $d(\mathcal{E})$ is the multidegree of the component $\mathcal{E}$ and $q^d = q_1^{d_1}q_2^{d_2}\dots$. \pauline{Find better notation.}

	When exploiting the row symmetries, since we don't compute only the homogeneous components of decreasing multidegree, we can not compute the character of $\GLr$ using such a summation. However, we know that if we have a component of multidegree $d=(d_1, d_2, \dots, d_k)$ , this correspond to a term $\sum_{\sigma \in \Sym{k}} q^{\sigma(d)} = m_d$ in the previous sum, thus we use monomials symmetric functions instead of summations to recover the character of $\GLr$ in each isotypic component.
	\pauline{Add time computation comparison (with and without optimisations) ?} \\

	For now we don't avoid to compute unnecessary homogeneous component since all we do is straighten the polynomials if they don't have decreasing multidegree. It would be even better if we could avoid completely computation of those polynomials. It is not possible for now because we don't know yet which operators should not been applied to avoid those polynomials.

@@

	Building on the previous strategy, it would be tempting to only compute the subspace of $sl_r$ highest weight vectors within each $\harmonics_k^P$.

>>>>

	\section{Introduction}
	In this article, we present a new SageMath package to compute bicharacter of some multivariate polynomials spaces. 
	The development of this package started at the occasion of a collaboration with François Bergeron to study the character of the space $\harmonics_n^{(r)}$ of diagonal harmonic polynomials on $r$ sets of $n$ variables, as a graded bi-$\GLr \times \Sn$-module. It was then extended to compute other characters of polynomial spaces.

	The main achievement is a calculation of the character of the diagonal harmonic polynomials for $n=6$ \pauline{+ some cases for $n=7$} and $r=5$ (and therefore any $r$) in 45 minutes (and ~15Gb), which led to conjectures on its general value.

@@

	Consider the polynomial ring $R=\QQ[X]$ with $r$ sets of $n$ variables. To fix conventions, we think of $X$ as a matrix of variables:
	$$(x_{i,j})_{0\leq i<r \atop 0\leq j<n}$$
	and we denote by $\bm{x}_i = (x_{i,1}, x_{i,2}, \dots, x_{i,n})$ the i-th set of variables. We use the convention that bold letters stand for sets of variables and light letters stand for the variables themselves.

	The polynomial ring $R$ is endowed with an action of the symmetric group $\Sn$ by diagonal permutation of the columns of $X$ and of the general linear group $\GLr$ by diagonal action on the rows of $X$. The invariant ring $R^{\Sn}$ is also known as the ring of multisymmetric functions, that is to say the elements of $R$ that remain unchanged under permutations of the rows of $X$. The co-invariant ring $R_{\Sn}$ is the quotient of $R$ by the ideal $\mathcal{I}_n = \langle {R^{\Sn^+}} \rangle$ of the multisymmetric functions without constant term. It inherits from $R$ a structure of graded $\GLr \times \Sn$ bi-module.

	The grading can be refined into a multigrading by rows. The multigrading is preserved by the action of $\Sn$. The multigrading is not preserved by the action of $\GLr$, but instead carries exactly the information about the $\GLr$-character. It is thus equivalent to consider the $\GLr \times \Sn$-bicharacter or the $\Sn$ multigraded character of $R_{\Sn}$.

@@

	Throughout this article, we implicitly use the Frobenius map, and identify $\Sn$ and $\GLr$ irreducible characters with their associated Schur functions. \\

	We denote the partial derivatives by $\partial^k_x := \frac{\partial^k}{\partial x^k}$ for all variables $x \in X$.
	When $X$ contains only one set of variables ($r=1$), $X = (x_1, x_2, \dots, x_n)$, we define the \emph{harmonic polynomials} as follow.

	\begin{definition}
		Let $f \in R$, $f$ is \emph{harmonic} if and only if, for all $k \geq 0$,
		$$\partial^k_{x_1} f + \partial^k_{x_2} f + \dots + \partial^k_{x_n} f = 0.$$
	\end{definition}

	The space of harmonic polynomials in $n$ variables, denoted $\harmonics_{n}$, is the joint kernel of the differential operators $D_k := \partial_{x_1}^k + \cdots + \partial_{x_n}^k$. It is also a realization of the coinvariants of the symmetric group: $R\, /\, \langle Sym(X)^+ \rangle$ and a graded regular representation of $\Sn$.

	\begin{example}
		The Vandermonde determinant $V_n:= \det(x_i^a)_{1 \leq i \leq n \atop 0 \leq a \leq n-1} = \prod_{i<j}(x_i-x_j)$ is harmonic.

		The space of harmonic polynomials in two variables is $\harmonics_2 = \langle 1, x_1-x_2 \rangle_\QQ$. 
	\end{example}

@@

	Going back to an arbitrary number $r$ of sets of variables, we define the \emph{differential operators} $(D_\alpha)_{\alpha\in \NN^r}$:
	$$D_{(\alpha_1, \dots, \alpha_r)} := \partial_{x_{1,1}}^{\alpha_1}\dots\partial_{x_{r,1}}^{\alpha_r} + \dots + \partial_{x_{1,n}}^{\alpha_1}\dots\partial_{x_{r,n}}^{\alpha_r}$$

	\begin{example}
		Take $r=3$ and denote $\bm{x}, \bm{y}$ and $\bm{z}$ the three sets of variables of $X$, then $D_{(3,0,4)} := \partial_{x_1}^3\partial_{z_1}^4 + \dots + \partial_{x_n}^3\partial_{z_n}^4$. 
	\end{example}

@@

	As for harmonic polynomials, we have an alternative way to obtain $\harmonics_n^{(r)}$ directly using operators.

@@

	Let $\bm{x}=(x_1, x_2, \dots, x_n)$ and $\bm{y}=(y_1, y_2, \dots, y_n)$ be two sets of variables and $\lambda$ be a partition of $n$. We also denote $\lambda$ the Ferrer's diagram (in French notation) associated to the partition $\lambda$ and each cell of $\lambda$ is given by the Cartesian coordinates $(a,b)$ of its bottom left corner. Then, let define
	$$M_{\lambda} := \det (x_i^ ay_i^ b)_{1 \leq i \leq n \atop (a,b) \in \lambda}$$
	and the Gasia-Haiman module associated to $\lambda$ is the smallest subspace containing $M_{\lambda}$ and closed under differentiation for both sets of variables. \\

	With a similar idea, François Bergeron recently introduced another generalization of the diagonal harmonics, with \emph{inert variables}. We add a new row $\bm{\theta} = (\theta_1, \theta_2, \dots, \theta_n)$ of variables in $X$ and call them inert. The symmetric group still acts by permutation of the columns of $X$, but $GL_r$ now acts diagonally only on the $r$ rows containing non-inert variables.

@@

	We first need to compute in a quotient by an ideal, $R / \mathcal{J}_n$ where $\mathcal{J}_n = \langle Sym(X)^+ \rangle$ is the ideal of diagonal symmetric polynomials on $r$ sets of $n$ variables.
	A standard approach would be to compute a Gröbner basis of this ideal.
	We haven't actually tried it, but given the number of variables and dimension of the quotient, we expect this calculation to be intractable.

@@

	At this stage, we have an algorithm, but are still doing linear algebra in a huge space. The cost is $N^2 M$, where $N$ is the dimension of the result and $M$ the dimension of the ambient space.

@@

	\begin{example} Compute $\mathcal{E}_{2,1}^{(2)}$ using the multidegree. 
		\begin{sagesilent}
			load("../compute_character.py")
		\end{sagesilent}
		First, we compute $\mathcal{E}_{2,1}^{(1)}$, for one row of variables. 
		\begin{sagecommandline}
			sage: v = vandermonde(Partition([2,1]))
			sage: v
			sage: derivatives = partial_derivatives(v.parent())
			sage: derivatives
			sage: E_21 = Subspace({v.multidegree(): [v]}, derivatives)
			sage: E_21.basis()
			sage: E_21.dimension()
		\end{sagecommandline}
		Then, we use polarization operators to introduce a second set of variables, and thus obtain $\mathcal{E}_{2,1}^{(2)}$, still with multidegree. 
		\begin{sagecommandline}
			sage: polarizators = polarization_operators(2)
			sage: polarizators
			sage: E_21 = PolarizedSpace(E_21, polarizators)
			sage: E_21.basis()
			sage: E_21.dimension()
			sage: E_21.dimensions()
		\end{sagecommandline}
		Compared with example \ref{H_3} in which all basis elements are grouped in one list with key $0$, here basis elements are classified by multidegree with the corresponding key. Operators are also separated by multidegree. Moreover, we have access to dimension by multidegree. 
	\end{example}

@@

	The $\GLr$-character can easily be recover from the multigrading, but it remains to find an efficient way to compute the representations of $\Sn$. Computing the traces of the action of permutations of all cycle types would not be an option because of the dimension and the high number of terms of the polynomials. 
	Instead, we use an isotypic projector to obtain the isotypic components of $\Sn$ and from that we will be able to recover the irreducible characters of $\Sn$ with their multiplicities. \\

	We first define two elements of the symmetric group algebra $\CC \Sn$. Note that we use the cyclic notation for permutations.
	Let $P_{\mu}$ be the subgroup of $\Sn$ of all row preserving permutations of $\mu$ and $Q_{\mu}$ the subgroup of the column preserving permutations of $\mu$. To determine the row and column preserving permutations, we consider the canonical Young tableau of $\mu$, that is to say the tableau filled in by integers from $1$ to $n$ in increasing order, from left to right and from bottom to top.

@@

	\begin{example} Consider $\Sym{3}$ and let $\mu = 2,1$.
		The canonical tableau associated is \tableau(12,3).\\
		Then $P_\lambda = \{1, (12)\}$ and $Q_\lambda = \{1, (13)\}$.

		For $\mu=2,1$, we have
		$a_{2,1} = 1 + (12)$ and
		$b_{2,1} = 1 - (13)$.

@@

		For the other partitions of size $3$, one can verify that 
		$c_{1,1,1} = \sum_{\sigma \in \Sym{3}} \sigma$ and 
		$c_{3} = \sum_{\sigma \in \Sym{3}} \sgn(\sigma)\sigma$.
	\end{example}

@@

	The proof of the above theorem is given by Fulton and Harris in \cite{FultonHarris1991}. 
	This theorem guarantees that $c_{\lambda}$ is an isotypic projector and that applying it on an adapted basis of $\mathcal{E}_{\lambda}$ gives representatives of the isotypic components of $\Sn$. \pauline{Need more details here.}  \\

@@

	However, since we use the Young symmetrizer to construct $\mathcal{E}_\lambda$, for all $v \in \mathcal{E}_\lambda$, $v$ is anti-symmetric with respect to the column stabilizer $Q_\mu$, with $\mu$ the type of the isotypic component of $v$. Indeed, when projecting a polynomial $p$ on its isotypic component using the Young idempotent $c_\mu$, by definition $p.a_\mu$ is symmetric with respect to the row preserving permutations of $\mu$ and then $v = p.a_\mu.b_\mu$ is anti-symmetric with respect to the column preserving permutations of $\mu$. 
	It's therefore sufficient to keep one representative monomial per $S_P$ orbit \pauline{$S_P$ orbit?} (and do some appropriate straightening whenever a new monomial is created). We chose to keep the smallest representative monomial in lexicographic order and call the result the \emph{normal reduced form} of $v$. \\

@@

		$\Delta_{21} = -x_{2} \theta_{1} + x_{3} \theta_{1} + x_{1} \theta_{2} - x_{3} \theta_{2} - x_{1} \theta_{3} + x_{2} \theta_{3}$ is type $1,1,1$ and has reduced form $x_1\theta_2$.

		$\partial_{x_2}\Delta_{21} = -\theta_1 + \theta_3$ is type $2,1$ and has reduced form $-\theta_1$.
	\end{example}

@@

	To achieve this, polarization operators can be tweaked. Whenever the result of a polarization is not of decreasing multidegree, straighten it by applying an appropriate permutation of the rows. It can then easily be shown that those tweaked polarization operators properly generate the whole $\mathcal{E}_\lambda^{(r)}$ space from $\mathcal{E}_\lambda^ {(1)}$. \pauline{Tweaked polarizators don't generate the whole space only the decreasing multidegree components.}

@@

	In practice, when we polarize $\mathcal{E}_\lambda^{(1)}$, tweaked polarization operators are given in argument to \texttt{PolarizedSpace} instead of the classical ones. As said above, when specifying the row symmetries, only components of decreasing multidegree appear in the final result.

@@

	As said before, the $\GLr$-character of $\mathcal{E}_\lambda$ is given by the multidegree of the homogeneous components. In other words, for a given isotypic component $\mathcal{E}_{\lambda,\mu}$, the $\GLr$-character associated to this component is given by $\sum_{\mathcal{E}_{\lambda,\mu}^{\langle d \rangle}} q^{d}$ where the sum is over all homogeneous component $\mathcal{E}_{\lambda,\mu}^{\langle d \rangle}$ of type $\mu$ and multidegree $d$ and $q^d = q_1^{d_1}q_2^{d_2}\dots$.

	When exploiting the row symmetries, since we don't compute only the homogeneous components of decreasing multidegree, we can not compute the character of $\GLr$ using such a summation. However, we know that if we have a component of multidegree $d=(d_1, d_2, \dots, d_k)$ , this correspond to a term $\sum_{\sigma \in \Sym{k}} q^{\sigma(d)} = m_d$ in the previous sum, thus we use monomials symmetric functions $m_d$ instead of summations to recover the character of $\GLr$ in each isotypic component.
	\pauline{Add time computation comparison (with and without optimisations) ?} \\

	For now we don't avoid compute some unnecessary homogeneous component since all we do is straighten the polynomials if they don't have decreasing multidegree. It would be even better if we could avoid completely the computation of those polynomials. It is not possible for now because we don't know yet which operators should not been applied to avoid those polynomials.

@@

	\pauline{I changed nothing in the two following subsections.}
	Building on the previous strategy, it would be tempting to only compute the subspace of $sl_r$ highest weight vectors within each $\harmonics_k^P$.
